\documentclass[a4paper,12pt]{article} 
\usepackage{times}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,nohead]{geometry}
\usepackage{graphics}

\begin{document}
\renewcommand{\rmdefault}{ptm}
\pagestyle{empty} 

\setlength{\parindent}{0mm} 
\setlength{\parskip}{5mm}

\begin{flushright}
\today
\end{flushright}

\emph{To:}\newline
Dr. Jerzy A. Filar\newline
Editor-in-Chief\newline
Environmental Modeling and Assessment, Springer

\emph{From:}\newline
Dr. Marcus W. Beck\newline
ORISE Research Participation Program\newline
US Environmental Protection Agency\newline
beck.marcus@epa.gov, 850-934-2480\vspace{14.5pt}

Enclosed please find our manuscript, entitled `Adaptation of a weighted regression approach to evaluate water quality trends in an estuary', to be considered as an original research article in Environmental Modeling and Assessment.  In many cases, the relatively simple methods that have been used to evaluate trends in environmental data in estuaries are often not sufficient to disaggregate the effects of multiple environmental drivers, limiting the potential to relate changes to possible causes.  To improve the description of long-term changes in water quality, we adapted a weighted regression approach developed to describe trends in pollutant transport in rivers to analyze a long-term water quality dataset from Tampa Bay, Florida. This is the first application of the technique to estuaries and we believe that our manuscript presents novel results that build on previous analyses, in addition to providing a generic method to be used  by others with similar datasets.

All authors have contributed equally to the content of the manuscript and have approved the submitted product.  Please note that Dr. Robert Hirsch, developer of the method, has already provided us with a review of an earlier draft of the mansucript.  Additionally, we have compiled the manuscript using a \LaTeX\ document preparation system with the Springer template and can provide source files if needed.  We greatly appreciate the opportunity to publish our work in Environmental Modeling and Assessment.\vspace{0.5in}

\hspace{4.5in}Respectfully,

\hspace{4.5in}Marcus W. Beck

\end{document}